\subsubsection{Scope}
This section describes the concept of operations for providing large-scale access to organizations.

\subsubsection{Overview}

\paragraph{Description}

The Bulk Export Service provides access to files containing LSST formal data products, as specified in the DPDD, for organized collaborations of authorized users and
participating institutions supporting authorized users.

\paragraph{Objective}

\begin{enumerate}

\item Provide large-scale data access to organizations entrusted to hold large
amounts of data before it is released to the worldwide astronomy community.

\item Provide large-scale data access to designated organizations for data after
it is released to the worldwide astronomy community..

\end{enumerate}

\paragraph{Operational Context}
The Bulk Export Servivce is available at NCSA only.

\paragraph{Risks}

\begin{enumerate}

\item An organization may attempt to access data other than the data agreed to.

\item If the form of delivered files is not standard format that is generally readable, users of the service may not find the
service useful.

\item Information may be lost, compared to information available through the Data Access Centers.

\end{enumerate}

\subsubsection{Operational Concepts}

\paragraph{Normal Operations}

During normal opertions, each site will have a MoU with LSST identifying the datasets and the due diligence required on the receiving site. The Authentication and Authorization system will be used to authenticate sites performing the data transfer.

\paragraph{Operational Scenarios}

Example use cases of the Bulk Export Service include:

\begin{enumerate}

\item Distribution of datasets of interest to the Dark Energy Science Collaboration.

\item Distribution of datasets of interest to the independent data access center at CC-IN2P3. However, forwarding of raw data to CC-IN2P3 is logically part of the data backbone functionality, and the return of data products computed at satellite computing facilties is the responsibility of the workload management system.

\end{enumerate}
