\subsubsection{Scope}

This section describes the concept of operations for archiving designated raw data acquired from the main LSST camera to the permanent archive.

\subsubsection{Overview}

\paragraph{Description}

The LSSTCam Archiving Service acquires pixel and header
data and arranges for the data to arrive in the Observatory
Operations Data Server and in the Data Backbone.


\paragraph{Objective}

The objective of this system is to acquire designated raw data from
the LSST main camera and header data from the OCS system, and to
place appropriately formatted data files in the Data Backbone. The
service needs to have the capability of archiving at the nominal frame
rate for the main observing cadence, and to perform ``catch up'' archiving
at twice that rate.

\paragraph{Operational Context}

LSSTCam Archiving is a service provided by LDF as part of the
prompt processing system. It is presented to Observatory Operations as an
OCS-commandable device. The archiving system operates independently
from related observatory services, such as data acquisition, as well as other
prompt services, such as prompt processing.  However, a normal
operational mode is operation of the service such that data are
ingested promptly into the permanent archive and into the Observatory Operations
Data Server for fast-access by Observatory Operations staff.

\subsubsection{Operational Concepts}

\paragraph{Normal Operations}

The LSSTCam Archiving Service runs whenever it is needed. Operational goals are
to provide prompt archiving of camera data and to provide expeditious
catch-up archiving after service interruptions.

LSSTCam data is, by default, ingested into the permanent archive
and into the Observatory Operations Data Server. However, while all
science and calibration data from the main camera require ingest into
the Observatory Operations Server, some data (e.g., one-off
calibrations, engineering data, smoke test data, etc.) may not require
archiving in the Data Backbone permanent store. Observatory Operations may
designate data which will not be archived.

\paragraph{Operational Scenarios}

\subparagraph{Delayed Archiving}

In delayed archiving, Observatory Operations may need to prioritize
the ingestion of data into the archiving system based on operational
dependencies with the Observatory Operations Data Service. The
archiving service provides a number of policies (which are TBD) to
Observatory Operations that can be selected via the OCS interface in order to
prioritize data ingestion.

Other operational parameters of interest include rate-limiting when network
bandwidth is a concern.

\subparagraph{Change Control}

Upgrades to the LSSTCam Archiving Service are produced in the LSST Data Facility.
Change control of this function is coordinated with the Observatory, with the
Observatory having an absolute say about insertion and evaluation of changes.
