\subsubsection{Scope}

The OCS-driven Batch Service provides an OCS-commandable device for Observatory
Operations staff to submit batch jobs to the Commissioning Cluster, NCSA cluster, or Base cluster, and optionally return a small amount of data via the Telemetry Gateway.

\subsubsection{Overview}

The service provides a method for OCS script to invoke Batch
production, allowing for the automation of batch procesing into simple work
flows involving LSST instrumentation.


\paragraph{Description}

The service provides OCS commands to initiate Batch Jobs and to optionally
return with small amounts of data as telemetry.

\paragraph{Objective}

Primary usage is expected to be preparation of daily master calibration images.  Full-frame wavefront sensing via pistoning of the Camera can also be processed in this mode.  Other uses are expeced during Commissioning.  Examples of the type of workflows may be verification of flats or wave-front sensing application.


\paragraph{Operational Context}

The service is an OCS-commandable device which runs under the control of
Observatory  Operations.

\subsubsection{Operational Concepts}

\paragraph{Normal Operations}

During normal operations, the OCS scripts submit batch jobs. The subject batch systems attempt to dispatch jobs at high priority.

\paragraph{Operational Scenarios}

The promptness of the return of results varies according to the ablity
of the batch system to schedule the coresponding batch job promptly.

\subparagraph{Change Control}

Upgrades to the OCS-driven Batch Service are produced by the LSST Data Facility. Change control
of this function is coordinated with the Observatory, with the Observatory having an absolute say
about insertion and evaluation of changes.
